---
title: "Iterating Contracts with R Markdown"
author: "Robert Cline"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
params:
  LeaseNo: 101.01
  FirstName: David
  LastName: David
  Address: P.O. Box 13  
  City: Chattanooga
  State: Georgia
  PostalCode: 37421
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)  

 
library(tidyverse)
library(ggplot2)
library(readr)
```


### Resources
* [**David Keyes Parameterized Reporting**](https://rfortherestofus.com/2020/10/parameterized-reporting-with-rmarkdown/)  
* [**Iterated fact sheets with R Markdown**, from Data@Urban published in Medium.com](https://medium.com/@urban_institute/iterated-fact-sheets-with-r-markdown-d685eb4eafce)  

* [Youtube Parameterized reports by Ashutosh Nandeshwar](https://www.youtube.com/watch?v=m1NLfvDWaNE&t=591s) See 23 minutes "network data".  You can find all the code along with the complementary blog post on my site here: [Ashutosh Nandeshwar's blog](http://nandeshwar.info/data-science-2/how-to-create-automated-analysis-using-r/)

``

This report is about the driving habits of the state of `r params$state'.

### Import Data
```{r}
library(readr)
parameters <- read_csv("../data/parameters.csv") %>% 
  distinct(LeaseID, .keep_all = TRUE) %>% 
  rename(State = StateOrProvince) %>%
  select(1:10)
View(parameters)
```



```{r}
library(readr)
tblLseTracts <- read_csv("../data/tblLseTracts.csv", 
    col_types = cols(CountyID = col_skip()))
View(tblLseTracts)
```

`

```{r}
# Set Parameters
parameters <- parameters %>%
    filter(LeaseNo == params$LeaseNo)

```


```{r}
# drivers_subset <- bad_drivers %>%
#   filter(LeaseNo == params$state)
# 
# drivers_subset %>%
#   mutate(perc_distracted = 100 - perc_not_distracted) %>%  
#   select(state, perc_speeding, perc_alcohol, perc_distracted) %>%
#   gather(key = "key", value = "value", -state) %>%  # now use pivot longer
#   ggplot(aes(key, value)) +
#   geom_bar(stat = "identity", fill="forestgreen", alpha=0.3) +
#   scale_y_continuous(expand = c(0, 0), limits = c(0, 40)) +  
# #  remove_ticks() + # part of Urban Instutute ggplot package
#   labs(title = stringr::str_glue("Driver condition in fatal crashes in {params$state}"))
```


This report is created on `r format(Sys.time(), '%d %B, %Y')` and covers **LeaseNo `r params$LeaseNo`**.  


Lessor:  `r params$FirstName` `r params$LastName`  
Address: `r params$Address`  
City: `r params$City`  
State: `r params$State`  
Zip Code: `r params$PostalCode`