---
title: "Applying Data Viz  and Markdown Concepts"
author: "CT"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.width = 10)
```

# Student Satisfaction Survey

Hi David. These are just a few mockups I created after taking the advanced data viz lessons. If you might happen to have a few minutes to look over the questions I've listed below, I'd greatly appreciate it. 

```{r}
library(tidyverse)
library(forcats)
library(scales)
library(readxl)
library(extrafont)

loadfonts()
```

## Functions Are Awesome

The use of functions to automate repetitive data-cleaning procedures has been a **life-saver** and I've *already* employed it in my work. Thank you!

```{r}
test <- read_xlsx("Themes Test.xlsx")

test <- test %>% 
  pivot_longer(cols = c(2:4),
               names_to = "response",
               values_to = "proportion") %>% 
  mutate(proportion_display = percent(proportion, accuracy = 1)) %>% 
  mutate(response = 
           fct_relevel(response,
                       "Strongly disagree or disagree",
                       "Neither agree nor disagree",
                       "Agree or strongly agree"
           ))

clean_data <- function(data){
  data %>% 
    pivot_longer(cols = c(2:4),
                 names_to = "response",
                 values_to = "proportion") %>% 
    mutate(proportion_display = case_when(
      proportion > 0.05 ~ percent(proportion, accuracy = 1),
      TRUE ~ "")) %>% 
    mutate(response = 
             fct_relevel(response,
                         "Strongly disagree or disagree",
                         "Neither agree nor disagree",
                         "Agree or strongly agree"
             ))
}

```

## Visual 1

Here is the first visual. Please see my questions below:

1. Can I adjust the legend position so that it still displays horizontally, but no legend entries are cut off?

1. After some googling around, I used scale_fill_manual to define the colours of the bars. Is there a better approach you might suggest for bar/column charts? (please refer to the code)

1. I also found a stackoverflow thread about how to position the labels (please see 'position=position_stack(vjust=0.5)' in the geom_text function). It does exactly what I want, but I'm not certain how it actually works! Have you used this before?


```{r}
gplot <- function(start_data){
  
  start_data %>% 
    # mutate(question = str_wrap(question, 15)) %>% 
    ggplot(aes(x = question,
               y = proportion,
               fill = response)) +
    geom_col(width = .5) +
    scale_y_continuous(label = percent_format(),
                       limits = c(0,1)) +
    coord_flip() +
    theme(text = element_text(size = 14, family="Inter"),
          legend.position = "top",
          legend.title = element_blank(),
          legend.title.align = .5,
          legend.key.size = unit(4, "mm"),
          legend.box.just = c(1, 0),
          panel.background = element_blank(),
          axis.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          plot.title.position = "plot",
          axis.text.x = element_text(family = "Inter", face = "bold", size = 12)) +
    scale_fill_manual("response", values = c("#D3062F", "#ABAAA8", "#14C853")) +
    geom_text(aes(label = proportion_display),
              position=position_stack(vjust = 0.5),
              color = "white",
              fontface = "bold",
              size = 4.5) +
    labs(title = "Students' agreement with questions")
}

test %>% 
  gplot()


```

## Visual 2

Here is the second visual. Questions:

1. I've used a function to reproduce the same plot for a different set of questions on a different sheet. Is this a recommended approach or am I going a bit too far with creating functions?

1. There is one label I'd like to remove, the "1%" for the last item. Is there a way to prevent the display of labels corresponding to values < ~5%?

1. The last item "students thought the workload was reasonable" is a bit long. Is there a way to break it up onto two lines?


```{r}
test2 <- read_xlsx("Themes Test.xlsx",
                   sheet = "ver2")

test2 <- clean_data(test2)

test2 %>% 
  mutate(question = case_when(
    question == "Students thought the workload was reasonable" ~ "Students thought the\nworkload was reasonable",
    TRUE ~ question
  )) %>% 
  gplot()
```


